An Adolescent Mini-Neptune in the Kepler Field

### 2021-06-03 paper/ms.tex
minor

% Cluster Difference Imaging Photometric Survey. III.
% Rotation and Lithium in an Open Cluster Spanning 500\,Parsecs
\title{
  A 30 Million Year Old Mini-Neptune in the Kepler Field
}

@@

\begin{abstract}
  Kepler\,1627 is an active G8V star previously found to host a
  $3.56\pm 0.04\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star
  was selected for observation by the Kepler satellite because it is
  nearby and it resembles the Sun.  Combining data from the Gaia
  satellite with rotation periods from TESS, we show that Kepler\,1627
  is a member of the \cn.  Based on isochronal and gyrochronal
  evidence, the cluster is $30\pm XX$\,Myr old.  Based on archival
  NIRC2 imaging, we also note the existence of a low-mass stellar
  companion. Our analysis advances Kepler\,1627Ab as the youngest
  planet with a precise age detected by the main Kepler mission.
  Newly derived ages from Gaia offer the opportunity to significantly
  expand the census of age-dated planets -- we offer a literature
  concatenation of young stars to support this effort.  The properties
  of \pn\ may also help clarify how the orbits and atmospheres of the
  mini-Neptune planets evolve.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Zoomed view of the \sn\ light curve.}  
		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
		30 minute cadence.  The {\it top panel} shows the
		\texttt{PDCSAP} median-subtracted flux in units of
		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
		is induced by starspots and plages.  The model for the
		stellar variability (orange line) is subtracted in the {\it
			bottom panel}, revealing the transits of \pn, as well as other
		deviations from the stellar variability model.  The 
		Figure Set available online shows the entire 3.9 years of
		available data.
		\label{fig:lightcurve}
	}
\end{figure*}

@@

>>>>

% Cluster Difference Imaging Photometric Survey. III.
% Rotation and Lithium in an Open Cluster Spanning 500\,Parsecs
\title{
  An Adolescent Mini-Neptune in the Kepler Field
}

@@

\begin{abstract}
  Kepler\,1627A is an active G8V star previously found to host a
  $3.6\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  selected for observation by the Kepler satellite because it is
  nearby ($d\approx 333\,{\rm pc}$) and resembles the Sun.  Combining
  data from the Gaia satellite with rotation periods from TESS, we
  show that Kepler\,1627 is a member of the $35\pm 10$\,Myr old
  $\delta$~Lyr cluster.  Our analysis advances Kepler\,1627Ab as the
  youngest planet with a precise age detected by the main Kepler
  mission.  New ages from the combination of Gaia and TESS offer the
  opportunity to significantly expand the census of age-dated planets
  -- we offer a literature concatenation of young stars to support
  this effort.  Future studies of \pn\ may also help clarify how the
  orbits and atmospheres of the mini-Neptune planets evolve.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Zoomed view of the \sn\ light curve.}  
		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
		30 minute cadence.  A one hundred day segment is shown here.  The {\it top panel} shows the
		\texttt{PDCSAP} median-subtracted flux in units of
		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
		is induced by starspots and plages.  The model for the
		stellar variability (orange line) is subtracted in the {\it
			bottom panel}, revealing the transits of \pn, as well as other
		deviations from the stellar variability model.  The 
		Figure Set available online shows the entire 3.9 years of
		available data.
		\label{fig:lightcurve}
	}
\end{figure*}

@@

Could the planet be on a high obliquity orbit?
% * how do the spectroscopic vsini and the measured v_rot=2πRstar/Prot compare?
%   * Rstar=0.91+-0.05, 2.606 days gives vsini=17.6km/s (+/-0.97km/s)
% * spectroscopic vsini is 18.8 +/- 4.7km/s from Keck HIRES... "20km/s" from
%   TRES.
